Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2016-01-28 docs/papers/roofline_model/gocean_roofline.tex
roofline: add set-associativity data to table giving cache specs

\begin{table}
\begin{tabular}{|l|c|c|c|c|}
\hline
  \multicolumn{5}{|c|}{E5-1620 v.~2, 3.7GHz} \\
  \hline
LINPACK (GFLOPS) & \multicolumn{4}{c|}{28.32} \\
\hline
                 &  L1 Cache & L2 Cache & L3 Cache & Main memory \\
                 &   32 KB   & 256 KB   & 10 MB    &  --         \\
\hline
STREAM2 (GB/s)   &  160  &  61.0  & 46.0 &  20.5 \\
  \hline
\multicolumn{5}{|c|}{E5-2697 v.~2, 2.7GHz}  \\
\hline
LINPACK (GFLOPS) & \multicolumn{4}{c|}{25.41} \\
\hline
               & L1 Cache & L2 Cache & L3 Cache & Main memory \\
               &   32 KB  & 256 KB   & 30 MB    &  --         \\
\hline
STREAM2 (GB/s) & 132      & 59.0     & 40.0     &  20.2 \\
\hline
\end{tabular}
\caption{The STREAM2 (DAXPY) and LINPACK benchmark results for a
  single thread running on each of the two CPUs considered here.}
\label{TAB_stream_linpack}
\end{table}

>>>>

\begin{table}
\begin{tabular}{|l|c|c|c|c|}
\hline
  \multicolumn{5}{|c|}{E5-1620 v.~2, 3.7GHz} \\
  \hline
LINPACK (GFLOPS) & \multicolumn{4}{c|}{28.32} \\
\hline
&  L1 Cache & L2 Cache & L3 Cache & Main memory \\
$n$-way set associative & 8    & 8   & 10 & -- \\
Size                  &   32 KB/core   & 256 KB/core   & 10 MB    &  --         \\
\hline
STREAM2 (GB/s)   &  160  &  61.0  & 46.0 &  20.5 \\
  \hline
\multicolumn{5}{|c|}{E5-2697 v.~2, 2.7GHz}  \\
\hline
LINPACK (GFLOPS) & \multicolumn{4}{c|}{25.41} \\
\hline
               & L1 Cache & L2 Cache & L3 Cache & Main memory \\
$n$-way set associative & 8    & 8   & 20 & -- \\
Size           &   32 KB/core  & 256 KB/core   & 30 MB    &  --         \\
\hline
STREAM2 (GB/s) & 132      & 59.0     & 40.0     &  20.2 \\
\hline
\end{tabular}
\caption{The STREAM2 (DAXPY) and LINPACK benchmark results for a
  single thread running on each of the two CPUs considered here.}
\label{TAB_stream_linpack}
\end{table}
